Individual Specific Allele Frequency

### 2019-02-27 rick/1kGP_lukeMod.Rmd

```{r}
Pop = apply(head(chr22_mtx,1000), 1, function(x)
                    glm2(x 
                          ~ bas_dt$Population
                          + bas_dt$avg_qual))
```

>>>>

```{r}
t= list()
for(f in seq(1,10000)){
  t1 = chr22_mtx[f,]
  t2 = subset[f,]
  t[[f]] = glm(t1 ~ bas_dt$avg_qual + offset(t2))
}

```{r}
Pop = apply(head(chr22_mtx,10000), 1, function(x)
                    glm2(x 
                          ~ bas_dt$Population
                          + bas_dt$avg_qual))
```
